Renewal and stability in populations structured by remaining years of life

### 2016-11-29 ThanoRepro/ThanoRepro.tex
mostly tinkering around with text. Big structural changes to come!

Each of these elements is structured by
age, $a$. %The model can be approximated by observed data because
%age is typically known. % The survival function, $\ell(a)$, derives
%from a lifetable, usually based on age-specific event-exposure mortality rates,
%which require counts of decedents and an estimate of the
%population exposed to risk in the same chronological age classes.
Age in the growth factor, $e^{-ra}$, pertains to the passage of
time more than it does to chronological age (this is synchronous with birth
cohorts). The product of this growth factor and $\ell(a)$ gives a
function proportional to the stable age structure, $c(a)$, and it is often
intuitive to imagine these two elements together as one for this reason. Female
fertility rates, $m(a)$, are based on daughters born to mothers in this limited
single-sex model.  The age-wise product of $m(a)$ and $\ell(a)$
can be interpreted as net female fertility, and this
is sometimes written as $\phi(a)$. As with most demographic models and
measures, this abstraction of renewal lends itself to
commonly collected data because age is typically known.
% For the two essential rate componenents underlying the renewal
 % equation~\eqref{eq:lotka}, classification by chronological age is essentially given--- it is deterministic in the sense that time passed since birth is typically known by individuals. The kinds of errors in such classification are mostly due to innumeracy, rounding, exaggeration, and similar kinds of biases, but even in such cases, chronological age is fundamentally knowable.

>>>>

Each of these elements is structured by
age, $a$. %The model can be approximated by observed data because
%age is typically known. % The survival function, $\ell(a)$, derives
%from a lifetable, usually based on age-specific event-exposure mortality rates,
%which require counts of decedents and an estimate of the
%population exposed to risk in the same chronological age classes.
Age in the growth factor, $e^{-ra}$, pertains to the passage of
time more than it does to chronological age (this is synchronous with birth
cohorts). The product of this growth factor and $\ell(a)$ gives a
function proportional to the stable age structure, $c(a)$, and it is often
intuitive to imagine these two elements together as one for this reason. Female
fertility rates, $m(a)$, are based on daughters born to mothers in this limited
single-sex model.  The age-wise product of $m(a)$ and $\ell(a)$
can be interpreted as net female fertility, and this
is sometimes written as $\phi(a)$. As with most demographic models and
measures, this model of renewal is tractable with
commonly collected population and vital data because age is typically known.
% For the two essential rate componenents underlying the renewal
 % equation~\eqref{eq:lotka}, classification by chronological age is essentially given--- it is deterministic in the sense that time passed since birth is typically known by individuals. The kinds of errors in such classification are mostly due to innumeracy, rounding, exaggeration, and similar kinds of biases, but even in such cases, chronological age is fundamentally knowable.
